Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-23 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Add formatting and corrections

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Ref.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ the Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\lambda$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \lambda - \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \lambda + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

@@

    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon

@@

    \frac{\Gamma(\varepsilon_{n+1})

@@

    + \Gamma^2(\varepsilon_{n+1})

@@

    \frac{\Gamma(\varepsilon_{n})

@@

    + \Gamma^2(\varepsilon_{n})

@@

with $\Gamma(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. We already identified that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction. However, by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify

@@

Then using Fermi-Dirac distribution as our partial distribution function ($f$) for this system

@@

and by letting $\lambda = \varepsilon_F$, the expression for conductivity leads to

@@

$\gamma_n \equiv {\Gamma(\varepsilon_n)}/{\hbar \omega_0}$.
Same as above derivation we can derive the transverse conductivity in $y$-direction by using the current operator derived in Appendix D

>>>>

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Ref.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon

@@

    \frac{\tilde{{\Gamma}}(\varepsilon_{n+1})

@@

    + \tilde{{\Gamma}}^2(\varepsilon_{n+1})

@@

    \frac{\tilde{{\Gamma}}(\varepsilon_{n})

@@

    + \tilde{{\Gamma}}^2(\varepsilon_{n})

@@

with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. We already identified that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction. However, by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify

@@

Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for this system

@@

and by letting $\Pi = \varepsilon_F$, the expression for conductivity leads to

@@

$\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
Same as above derivation we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix D

### 2021-07-23 paper/v1.0/sections/6_manipulate_conductivity.tex
Add formatting and corrections

To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
transverse conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$. Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \frac{\sigma^{xx}}{\sigma^{0}} = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
where $\sigma^0 = (e^2/\pi \hbar A)$. We use this expression to illustrate the changes that can be done to the transverse conductivity in 2DEG using external dressing field. As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system. For a given dressing field intensity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values. Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values. In contrast, on Landau levels conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_4} the peak value of transverse conductivity on each Landau level gets increase with the Landau level number.

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}

Considering the effect of the external dressing field on transverse conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels. However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
These characteristics are aligned with results demonstrated by K. Dini et al.\cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_4} and \ref{fig_5} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional transverse conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result represented by A. Endo et al. \cite{endo09}.
The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range. However, they have not considered the tunability that can be achieved with the external strong dressing field. In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG, and we have presented a more generalized theory. As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.

>>>>

To identify the characteristics of the longitudinal conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$. Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \frac{\sigma^{xx}}{\sigma^{0}} = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
where $\sigma^0 = (e^2/\pi \hbar A)$. We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using external dressing field. As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system. For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values. Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values. In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_5} Normalized longitudinal conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_6} $3$rd Landau level’s normalized longitudinal conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}

Considering the effect of the external dressing field on longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels. However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
These characteristics are aligned with results demonstrated by K. Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result mentioned in Ref. \cite{endo09}.
The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range. However, they have not considered the tunability that can be achieved with the external strong dressing field. In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG, and we have presented a more generalized theory. As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.

### 2021-07-23 paper/v1.0/sections/7_conclusions.tex
Add formatting and corrections

In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. With the uniform magnetic field charged particles can only settle in discrete energy values and this leads to the Landau quantization. We modelled the behavior of electrons in Landau levels under the dressing field utilizing Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considering system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field. We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field. Furthermore, we identified that by regulating the intensity of radiation, the conductivity regions near Landau levels can be squeezed. Despite, this behavior has been identified previous works, their results are not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for  these special quantum Hall systems.

In summary, the primary purpose of this study were to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems. Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance and inventing novel appliance.

>>>>

In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. With the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization. We modelled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field. We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field. Furthermore, we identified that by regulating the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite, this behavior has been identified previous works, their results are not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for these special quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems. Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance and inventing novel appliance.
